---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gammaextremes

<!-- badges: start -->
[![codecov](https://codecov.io/gh/valcourgeau/extreme-trawl/branch/master/graph/badge.svg?token=DHLBP4BLP0)](https://codecov.io/gh/valcourgeau/extreme-trawl)
[![R-CMD-check](https://github.com/valcourgeau/extreme-trawl/workflows/R-CMD-check/badge.svg)](https://github.com/valcourgeau/ntwk/actions)
[![R-CMD-check](https://github.com/valcourgeau/extreme-trawl/workflows/R-CMD-check/badge.svg)](https://github.com/valcourgeau/extreme-trawl/actions)
<!-- badges: end -->

The goal of `extreme.trawl` is to provide statistical inference tools for univariate extreme time series.  It comprises pairwise and generalised method of moments inference strategies described in Courgeau and Veraart (2021) <doi:10.2139/ssrn.3527739> and simulation schemes based on Gamma-distributed trawl processes.

## Installation

*SOON* You can install the released version of `extreme.trawl` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("extreme.trawl")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("valcourgeau/extreme-trawl")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(extreme.trawl)
## basic example code
```
